---
title: "Reproducible Research: Peer Assessment 1"
author: "Jerrison Li"
output: html_document
keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(dplyr)
library(xtable)
```

## Loading and preprocessing the data

```{r loading}
unzipped_data <- unzip(paste0("/Users/jerrison/Coursera_Homework/",
                              "RepData_PeerAssessment1/activity.zip"))

step_data <- read.csv(unzipped_data, 
                      stringsAsFactors = FALSE)
```

## What is mean total number of steps taken per day?

1. Calculate the total number of steps taken per day

```{r steps_per_day}
step_data_by_day <- select(step_data,
                           date,
                           steps) %>%
  group_by(date) %>%
  summarize(steps = sum(steps, na.rm = T))

step_data_by_day

```

2. Histogram of total number of steps per day

```{r steps_by_day_histogram}

total_steps_per_day_histogram2 <- ggplot(step_data_by_day, 
                                        aes(x = date, y = steps)) +
  geom_bar(stat = "identity") +
  theme(axis.text.x = element_text(angle = 90))

total_steps_per_day_histogram2
```

3. Calculate and report the mean and median of the total number of steps taken 
per day

```{r mean_median_steps_per_day}
mean_median_per_day <- select(step_data,
                              date,
                              steps) %>%
  group_by(date) %>%
  summarize(mean_steps = mean(steps, na.rm = T),
            median_steps = median(steps, na.rm = T))

mean_median_per_day
```

## What is the average daily activity pattern?

1. Make a time series plot (i.e. ğšğš¢ğš™ğš = "ğš•") of the 5-minute interval (x-
axis) and the average number of steps taken, averaged across all days (y-axis)

```{r time_series_plot}
average_steps_per_interval <- select(step_data,
                                     interval,
                                     steps) %>%
  group_by(interval) %>%
  summarize(days_count = n(),
            total_steps = sum(steps, na.rm = T),
            average_steps = sum(steps, na.rm = T)/n())

average_steps_per_interval

average_steps_per_interval_plot <- ggplot(average_steps_per_interval,
                                          aes(x = interval, y = average_steps)) + 
  geom_line()

average_steps_per_interval_plot
```

2. Which 5-minute interval, on average across all the days in the dataset, 
contains the maximum number of steps?

```{r which_max}
max_step_interval <- average_steps_per_interval$interval[
  which.max(average_steps_per_interval$average_steps)]
```

Interval `r max_step_interval` contains the maximum number of steps on average.

## Imputing missing values

1. Calculate and report the total number of missing values in the dataset

```{r total_missing_values}
na_count <- sum(is.na(step_data$steps))
na_count
```

The total number of missing values is `r na_count`.

2. Devise a strategy for filling in all of the missing values in the dataset. 
The strategy does not need to be sophisticated. For example, you could use the 
mean/median for that day, or the mean for that 5-minute interval, etc.

My strategy is to use the mean for that 5-minute interval.

3. Create a new dataset that is equal to the original dataset but with the 
missing data filled in.

```{r step_data_modified}
step_data_modified <- left_join(step_data, )

```
## Are there differences in activity patterns between weekdays and weekends?
